Packaging research artifacts with RO-Crate

### 2021-05-14 content/80.formal-definition.tex
definition lists..

%% TODO: Being onverted to LaTex math mode. See GitHub rendering for original Unicode symbols
% https://github.com/stain/ro-crate-paper/blob/master/content/80.formal-definition.md

% Text remains for now as Markdown blocks

@@

\begin{markdown}
The domain of discourse $\mathbb{D}$ is the set of $\mathbb{IRI}$ identifiers [@doi:10.17487/rfc3987] (notation `<http://example.com/>`), with additional descriptions using numbers $\mathbb{R}$ (notation `13.37`) and literal strings $\mathbb{S}$ (notation `"Hello"`).

@@

The below is an example RO-Crate represented using the above formalization, assuming a base URI of `<http://example.com/ro/123/>`:

    ROCrate(<http://example.com/ro/123/>)
    name(<http://example.com/ro/123/, 
        “Data files associated with the manuscript:Effects of …”)
    description(<http://example.com/ro/123/, 
        “Palliative care planning for nursing home residents …")
    datePublished(<http://example.com/ro/123/>, “2017")
    license(<http://example.com/ro/123/>, 
        <https://creativecommons.org/licenses/by-nc-sa/3.0/au/>
    ContextualEntity(<https://creativecommons.org/licenses/by-nc-sa/3.0/au/>)
    name(<https://creativecommons.org/licenses/by-nc-sa/3.0/au/, 
        “Attribution-NonCommercial-ShareAlike 3.0 Australia (CC BY-NC-SA 3.0 AU)”)

    hasPart(<http://example.com/ro/123/>, <http://example.com/ro/123/file.txt>)
    File(<http://example.com/ro/123/survey.csv>)
    name(<http://example.com/ro/123/survey.csv>, “Survey of care providers”)
    hasPart(<http://example.com/ro/123/>, <http://www.example.om/ro/123/folder/>)
    Dataset(<http://example.com/ro/123/interviews/>)
    name(<http://example.com/ro/123/interviews/>, 
        “Audio recordings of care provider interviews”)
\end{markdown}

>>>>

%% TODO: Convert to LaTex math mode. See GitHub rendering for original Unicode symbols
% https://github.com/stain/ro-crate-paper/blob/master/content/80.formal-definition.md

% Text remains for now as Markdown

@@

\begin{markdown}
The domain of discourse $\mathbb{D}$ is the set of $\mathbb{IRI}$ identifiers [@doi:10.17487/rfc3987] (notation `<http://example.com/>`), with additional descriptions using numbers $\mathbb{R}$ (notation $13.37$) and literal strings $\mathbb{S}$ (notation $\text{“Hello”}$).

@@

The below is an example RO-Crate represented using the above formalization, assuming a base URI of `<http://example.com/ro/123/>`:
\end{markdown}

\allowdisplaybreaks
\begin{eqnarray*}
&& ROCrate(\texttt{<http://example.com/ro/123/>}) \\
&& name(\texttt{<http://example.com/ro/123/>}, \\
&& \ \ \ \ \ \text{“Data files associated with the manuscript:Effects of …”}) \\
&& description(\texttt{<http://example.com/ro/123/}, \\
&& \ \ \ \ \ \text{“Palliative care planning for nursing home residents …”}) \\
&& license(\texttt{<http://example.com/ro/123/>}, \\ 
&& \ \ \ \ \ \texttt{<https://creativecommons.org/licenses/by-nc-sa/3.0/au/>}) \\ 
&& datePublished(\texttt{<http://example.com/ro/123/>}, \text{“2017-02-23”}) \\ 
&& hasPart(\texttt{<http://example.com/ro/123/>}, 
        \texttt{<http://example.com/ro/123/file.txt>}) \\
&& hasPart(\texttt{<http://example.com/ro/123/>}, 
        \texttt{<http://www.example.om/ro/123/folder/>}) \\
\\
&& ContextualEntity(\texttt{<https://creativecommons.org/licenses/by-nc-sa/3.0/au/>}) \\
&& name(\texttt{<https://creativecommons.org/licenses/by-nc-sa/3.0/au/>},  \\
&& \ \ \ \ \  \text{“Attribution-NonCommercial-ShareAlike 3.0 Australia (CC BY-NC-SA 3.0 AU)”}) \\
\\
&& File(\texttt{<http://example.com/ro/123/survey.csv>}) \\
&& name(\texttt{<http://example.com/ro/123/survey.csv>}, 
        \text{“Survey of care providers”}) \\
\\
&& Dataset(\texttt{<http://example.com/ro/123/interviews/>}) \\
&& name(\texttt{<http://example.com/ro/123/interviews/>},  \\
&& \ \ \ \ \  \text{“Audio recordings of care provider interviews”}) 
\end{eqnarray*}

### 2021-05-14 latex/ro-crate.tex
Added Simone as co-author in latex
Sunday fun with tables in LaTeX
Fixed table
More LaTeX IsN'tiT
some blurb about DMPs
Reviews, credits, formal definitions in tex
definition lists..

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
% \usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
% \usepackage{graphicx}

\DeclareGraphicsExtensions{.pdf,.png,.svg}
\graphicspath{../content/images/}
\usepackage[citations,fencedCode,footnotes,hybrid,pipeTables,smartEllipses,tableCaptions,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

@@

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[D]{RO-Crate Community},
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\author[B]{\inits{P.G.}\fnms{Paul} 
\snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}
\address[D]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}

@@

\begin{abstract}
Abstract text.
\end{abstract}

@@

% Every *.md file in content/ in order, except 00, 90
\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/41.workflows.md}
\markdownInput{../content/42.regulatory.md}
\markdownInput{../content/43.culturalheritage.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/70.acknowledgements.md}

@@

\appendix
\markdownInput{../content/80.formal-definition.md}
% TODO: Recode formal definition to LaTeX math mode?
%\input{../content/80.formal-definition.tex}
\markdownInput{../content/89.community.md}

>>>>

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
% \usepackage{graphicx}

\DeclareGraphicsExtensions{.pdf,.png,.svg}
\graphicspath{../content/images/}
\usepackage[citations,definitionLists,fencedCode,footnotes,hybrid,pipeTables,smartEllipses,tableCaptions,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

% for table resizing
\usepackage{booktabs}
\usepackage{multirow}

@@

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[E]{\inits{S.L.}\fnms{Simone} \snm{Leo}\ead[label=e5]{simone.leo@crs4.it}\ead[label=o5,orcid]{0000-0001-8271-5429}},
\author[D]{RO-Crate Community},
\author[B]{\inits{P.G.}\fnms{Paul} 
\snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}
\address[E]{\orgname{Center for Advanced Studies, Research, and Development in Sardinia} (CRS4), Pula (CA), \cny{Italy}\printead[presep={\\}]{e5,o5}}
\address[D]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}

@@

\begin{abstract}
\markdownInput{../content/01.abstract.md}
\end{abstract}

@@

% Every *.md file in content/ in order, except 00, 90
\markdownInput{../content/10.background.md}

\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}

\input{../content/31.tooling-table.tex}
%\markdownInput{../content/31.tooling-table.md}
\markdownInput{../content/30.tooling.md}

\markdownInput{../content/40.inuse.md}
\markdownInput{../content/41.workflows.md}
\markdownInput{../content/42.regulatory.md}
\markdownInput{../content/43.culturalheritage.md}
\markdownInput{../content/44.dmp.md}

\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/70.acknowledgements.md}

@@

\appendix
\markdownInput{../content/80.formal-definition.md}
% TODO: Recode formal definition to LaTeX math mode?
%\include{../content/80.formal-definition}

\markdownInput{../content/89.community.md}
